#Project 1 Document
Claudio Freitas

##Section 1

This is the first code chunk to read the data file and transform data:


```{r, echo=TRUE}
library(plyr)
activity <- read.csv("./repdata-data-activity/activity.csv")
activity$date <- as.Date(activity$date)
activity$steps <- as.numeric(activity$steps)
activity$interval <- as.numeric(activity$interval)
apply(activity, 2, max, na.rm=T)

```

##Section2

Subset data, calculate total steps per day and plot histogram

```{r, echo=TRUE}
subdata <- ddply(activity, .(date), summarize, agregate = sum(steps))
hist(subdata$agregate,col="red",breaks=20,xlab="mean steps per day", main="Steps histogram")
meansteps <- format(mean(subdata$agregate, na.rm=T), nsmall=2)
mediansteps <- format(median(subdata$agregate,na.rm=T), nsamll=2)
```

The mean is `r meansteps` and the median is `r mediansteps`.

##Section 3

subset data to calculate average step for each interval and plot a linear chart

```{r, echo=TRUE}
subdata1 <- ddply(activity, .(interval), summarize, agregateX = mean(interval))
subdata2 <- with(activity, tapply(steps, interval, mean, na.rm=T))
plot(subdata1$agregateX, subdata2, type="l", xlab = "Time interval", ylab = "Number of Steps")
```

Calculate the interval with max average steps
```{r, echo=TRUE}
maxi <- max(subdata2)
maxint <- which.max(subdata2)
maxint<- subdata1$agregateX[maxint]
```

The maximum value for average number of steps in a particluar time interval is `r maxi`

The 5 minutes time interval for the maximum average number of steps is `r maxint`

##Section 4

Calculating the number of rows with NAs

```{r, echo=TRUE}
totalna<- sum(is.na(activity$steps))
print (totalna)
```

Create a new dataset without NAs

```{r, echo=TRUE}
totalna<- is.na(activity$steps)
subdata<- tapply(activity$steps, activity$interval, mean, na.rm=T)
activity$steps[totalna] <- subdata[as.character(activity$interval[totalna])]
```


Plot a histogram with the sum of the steps for each day
```{r, echo=T}
result<- tapply(activity$steps, activity$date, sum, na.rm=T)
hist(result, col="red",breaks=20, xlab="mean steps per day", main="Steps histogram")
mean1<- format(mean(result))
median1<- format(median(result))
```

The mean is `r mean1`

The median is `r median1`


##Section 5

Subseting weekday and weekend using the wekdays() function

```{r, echo=TRUE}
activity$day<- weekdays(as.Date(activity$date))
actwday<- subset(activity, !day %in% c("sabado", "domingo"))
actwend<- subset(activity, day %in% c("sabado","domingo"))
```

creating a panel with the two charts (weekend and weekdays)

```{r, echo=TRUE}
par(mfrow=c(1,2))
Yweekdays<- tapply(actwday$steps, actwday$interval, mean, na.rm=T)
Xweekdays<- tapply(actwday$interval, actwday$interval,unique, na.rm=T)
Yweekends<- tapply(actwend$steps, actwend$interval, mean, na.rm=T)
Xweekends<- tapply(actwend$interval, actwend$interval,unique, na.rm=T)
plot(Xweekdays, Yweekdays, type="l",xlab = "Weekdays activity", ylab = "Total steps")
plot(Xweekends, Yweekends, type="l",xlab = "Weekends activity", ylab = "Total steps")
```
